\pisodm: Building Service-Oriented Applications in the Presence of Non-Functional Requirements

### 2015-04-07 JournalToSubmit2015/relworks.tex
Small changes on Section 2.

While Functional Requirements establish \textit{what} is computed by an application, Non-Functional Requirements (NFRs) are concerned with \textit{how} the task is preformed.
NFRs include aspects such as performance, authentication and quality constraints.
These requirements are usually specified by conditions, called Non-functional Properties.
Non-functional properties are also referred to as constraints, quality attributes, quality goals, quality of service requirements and non-behavioral requirements~\cite{Chung91,MylopoulosBook99,Chung2009}.

@@

Beside the existence of these works, it is important to remark that authors continue emphasizing the limited attention of the model-driven proposals for service development to non-functional requirements~\cite{Ameller201542,Ameller2010}. As Ameller et al. realize in a recent published literature review that there are \textit{``Not many papers that presented a generic approach to deal with NFRs"}. Authors also remark in such study the lack of industrial use cases~\cite{Ameller201542}. 
Our method to develop service-oriented applications aims to cover this lack of proposals dealing with non-functional requirements and gives support to real needs, as presented in a company related to the risk assessment industry.

>>>>

While Functional Requirements establish \textit{what} is computed by an application, Non-Functional Requirements (NFRs) are concerned with \textit{how} the task is performed.
NFRs include aspects such as performance, authentication and quality constraints.
These requirements are usually specified by conditions, called non-functional properties.
Non-functional properties are also referred to as constraints, quality attributes, quality goals, quality of service requirements and non-behavioral requirements~\cite{Chung91,MylopoulosBook99,Chung2009}.

@@

Beside the existence of these works, it is important to remark that authors continue emphasizing the limited attention of the model-driven proposals for service development to non-functional requirements~\cite{Ameller201542,Ameller2010}. As Ameller et al. realize in a recently published literature review, there are \textit{``Not many papers that presented a generic approach to deal with NFRs"}. Those authors also remark the lack of industrial use cases~\cite{Ameller201542}. 
Our method to develop service-oriented applications aims to cover this lack of proposals dealing with non-functional requirements and gives support to real needs, as presented in a company related to the risk assessment industry.
